**Density Dependence**

### 2022-12-28 Rmd/runDD.Rmd
with eqns

Mackerel life history parameters are used to construct an `FLBRP` object to represent the equilibrium dynamics and then an `FLStock` object models the time series dynamics.

>>>>

Mackerel life history parameters are used to construct an example of modelling density dependence, first an `FLBRP` object is used  represent the equilibrium dynamics and then an `FLStock` object is constructed to models the time series dynamics.
